\documentclass[12pt]{article}
\title{how to prepare for IIT-JEE Examination ?}
\author{ kalyan dawar}
\date{\today}
\begin{document}
\maketitle

som
\section{what is JEE?}
jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. jee is an entrance examination to get into the top college of india. 
\subsection{Syllabus}
pyhsics,chemistry,Math
\subsection{competition level}
around 10 lack students appear for the examination
\section{how to perpare for mathematcis}
Learn the concepts of mathematics
\section{how to perpare for the Pyhsics}
Learn the basic formulae of pyhiscis
\section{how to prepare for chemistery }
learn the basic periodic table

 
\end{document}